Understanding Structure and Selectivity in Nanostructured Lyotropic Liquid Crystal Membranes using Molecular Simulations

### 2020-04-27 Ben_Manuscripts/thesis/stochastic_transport.tex
spell checking and mod to usage of subdiffusion

\documentclass[aps,pre,preprint,groupedaddress,longbibliography]{revtex4-2}
\usepackage{CJK}

\usepackage{multirow}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{subcaption}
%\usepackage{caption}
\usepackage{amsmath} % or simply amstext
\usepackage{amssymb}
\usepackage{siunitx}
\usepackage{booktabs}
\usepackage[export]{adjustbox}
\usepackage{cleveref}
\usepackage{booktabs}
\usepackage{gensymb}
\usepackage{float}
\usepackage{xr}
\usepackage{diagbox}
\usepackage{array}

\DeclareUnicodeCharacter{03C9}{$\omega$}
%\usepackage[en]{babel}

\newcolumntype{P}[1]{>{\centering\arraybackslash}p{#1}}
\newcolumntype{M}[1]{>{\centering\arraybackslash}m{#1}}
\newcommand{\PreserveBackslash}[1]{\let\temp=\\#1\let\\=\temp}
\newcolumntype{C}[1]{>{\PreserveBackslash\centering}p{#1}}
\newcolumntype{R}[1]{>{\PreserveBackslash\raggedleft}p{#1}}
\newcolumntype{L}[1]{>{\PreserveBackslash\raggedright}p{#1}}

\externaldocument[S-]{Supporting_Information}

\begin{document}

  \title{Capturing Subdiffusive Solute Dynamics and Predicting Selectivity in Nanoscale Pores
  with Time Series Modeling}

  \author{Benjamin J. Coscia}
  \author{Michael R. Shirts}

  \affiliation{Department of Chemical and Biological Engineering, University of Colorado Boulder, Boulder, Colorado 80309, United States}

  \date{\today}

  \begin{abstract}

  Mathematically modeling complex transport phenomena at the molecular level 
  can be a powerful tool for identifying transport mechanisms and predicting
  macroscopic properties. We use two different stochastic time series models,
  parameterized from long molecular dynamics (MD) simulation trajectories of
  a cross-linked H\textsubscript{II} phase lyotropic liquid crystal (LLC) 
  membrane, in order to predict solute mean squared displacements (MSDs) 
  and solute flux, and thus solute selectivity, in macroscopic length pores.

  First, using anomalous diffusion theory, we show how solute dynamics can be
  modeled as a fractional diffusion process subordinate to a continuous time 
  random walk. From the MD simulations, we parameterize the distribution of 
  dwell times, hop lengths between dwells and correlation between hops. We 
  explore two variations of the anomalous diffusion modeling approach. The first variation
  applies a single set of parameters to the solute displacements and the second
  applies two sets of parameters based on the solute's radial distance from the
  closest pore center.

  Next, we generalize Markov state models, treating the
  configurational states of the system as a Markov process where each
  state has distinct transport properties. For each state and transition
  between states, we parameterize the distribution and temporal correlation 
  structure of positional fluctuations as a means of characterization and to 
  allow us to predict solute MSDs. We show that both models reasonably reproduce
  the MSDs calculated from MD simulations. However, qualitative differences 
  between MD and Markov state dependent model-generated trajectories may limit 
  its usefulness.

  Finally, we demonstrate how one can use these models to 
  estimate flux of a solute across a macroscopic-length pore and, based on 
  those quantities, the membrane's selectivity towards each solute. This work 
  helps to connect microscopic chemically-dependent solute motions that do not
  follow simple diffusive behavior with macroscopic membrane performance.

  \end{abstract}

  \maketitle

  \graphicspath{{./figures/}}

@@

  Highly selective separations membranes are desirable in numerous
  applications. The ability to efficiently separate ions from saline water
  sources using membranes has been actively pursued for years in an effort to
  create potable water for people in water-scarce
  regions.~\cite{werber_materials_2016} Even in relatively safe municipal water
  supplies, there is a need for membranes that can specifically separate
  potentially harmful organic micropollutants such as fertilizers, pesticides,
  pharmaceuticals and personal care products.~\cite{barbosa_occurrence_2016} In
  the materials industry, there is a strong interest in creating breathable
  fabrics which selectively allow passage of water
  vapor.~\cite{mondloch_destruction_2015}

  Lyotropic liquid crystals (LLCs) are a class of amphiphilic molecules that
  can be cross-linked into mechanically strong and highly selective nanoporous
  membranes.~\cite{gin_polymerized_2008} They may provide a promising
  alternative to conventional membrane separation techniques by being selective
  based not only on solute size and charge, but on solute chemical
  functionality as well.~\cite{dischinger_application_2017} One can tune the
  functionality of LLC monomers in order to enhance or weaken specific
  solute-membrane interactions.~\cite{dischinger_effect_2017} Two general
  morphologies of LLC membranes are being actively developed. The inverted
  hexagonal, H\textsubscript{II}, LLC phase has densely packed, uniform-sized
  pores on the order of 1 nm in size. A perfectly synthesized
  H\textsubscript{II} phase has an ideal geometry for high throughput
  separations. Unfortunately, aligning the microscopic hexagonal mesophases on
  a large scale as required for high permeability has shown limited
  success.~\cite{feng_scalable_2014,feng_thin_2016} Bicontinuous cubic,
  Q\textsubscript{I}, phase LLC membranes share the uniform and nm-sized chemically
  complex pores of the H\textsubscript{II} phase but its geometry consists of a
  tortuous network of 3D interconnected pores which do not require
  alignment.~\cite{carter_glycerol-based_2012} While its pore structure may
  decrease a Q\textsubscript{I} phase membrane's permeability relative to the
  H\textsubscript{II} phase, it is considerably easier to produce 
  at scale.~\cite{hatakeyama_nanoporous_2010}

  Molecular modeling may make it possible to efficiently evaluate
  solute-specific separation membranes using the available chemical space of
  LLC monomers. To date, only a limited subset of LLC monomers have been
  studied experimentally in membrane applications.
  \cite{carter_glycerol-based_2012,hatakeyama_nanoporous_2010,smith_ordered_1997,zhou_assembly_2003,resel_structural_2000}
  Even within this small subset, they have demonstrated selectivities that
  could not be explained beyond speculation and vague empirical
  correlations.~\cite{dischinger_application_2017} Atomistic molecular modeling
  can provide the resolution necessary to identify molecular interactions that
  are key to separation mechanisms, allowing us to move beyond Edisonian design
  approaches.

  In our previous work,~\cite{coscia_chemically_2019} we used molecular
  dynamics (MD) simulations to study the transport of 20 small polar molecules
  in an H\textsubscript{II} phase LLC membrane. We chose to study the
  H\textsubscript{II} phase because it is a simpler geometry to model than the
  Q\textsubscript{I} phase and significantly more structural data is available
  to help ensure molecular models are consistent with experiment. In general,
  we observed subdiffusive transport behavior characterized by intermittent
  hops separated by periods of entrapment. We identified three mechanisms
  responsible for the solute trapping behavior: entanglement among monomer
  tails, hydrogen bonding with monomer head groups, and association with the
  monomer's sodium counter ions.

@@

  We constructed our first model by applying the existing rigorous theoretical
  foundation which describes the motion of particles that exhibit non-Brownian,
  or anomalous, transport behavior.~\cite{metzler_random_2000,bouchaud_anomalous_1990} The tools
  introduced by fractional calculus are instrumental to this
  theory.~\cite{gorenflo_fractional_1997} They allow us to generalize the
  normally linear diffusion equation to fractional derivative orders, providing
  descriptions of a much more diverse set of behavior, including subdiffusion,
  a type of anomalous diffusion exhibited by solutes in this
  study.~\cite{klages_anomalous_2008}

@@

  We ran all MD simulations and energy minimizations using GROMACS
  2018~\cite{bekker_gromacs:_1993,berendsen_gromacs:_1995,van_der_spoel_gromacs:_2005,hess_gromacs_2008}.
  We performed all post-simulation trajectory analysis using Python scripts
  which are available online at \\
  \texttt{https://github.com/shirtsgroup/LLC\_Membranes}.  The appropriate
  scripts to use for subsequent calculations are summarized in
  Table~\ref{S-table:python_scripts} of the Supplemental Material.

@@

  We considered each system to be equilibrated when the solute partitioning between the 
  pore and tail region reached apparent equilibrium and use only data after that point
  in our analysis of solute kinetics. We plot the solute partition versus time in
  Figure~\ref{S-fig:equilibration} of the Supplemental Material in order to justify
  our choice of equilibration times for each solute.

@@

  Solutes in this system very clearly exhibit subdiffusive behavior, a type of
  anomalous diffusion. During an anomalous diffusion process, the mean squared 
  displacement (MSD) does not grow linearly with time, but instead it follows 
  a power law of the form: 
  \begin{equation} 
  \langle z^2(t) \rangle = K_{\alpha}t^{\alpha}
  \label{eqn:msd_form}
  \end{equation} 
  where $\alpha$ is the anomalous exponent and $K_{\alpha}$ is the generalized 
  diffusion coefficient. In this work, we only consider the MSD with respect to
  the solutes' center of mass $z$-coordinate, which is oriented along the pore 
  axis. A value of $\alpha < 1$ indicates a subdiffusive process, while values
  of $\alpha = 1$ and $\alpha > 1$ are characteristic of Brownian and 
  superdiffusive motion respectively.

  While it is theoretically possible to extract the value of $\alpha$ by fitting
  Equation~\ref{eqn:msd_form} to an MSD generated directly from MD simulations, 
  we do not simulate enough independent solute trajectories to obtain a reliable
  estimate. We can obtain higher precision estimates of $\alpha$ using the dwell
  time distributions described in subsequent sections.

@@

  One can measure MSD in two ways. The ensemble averaged MSD measures 
  displacements with respect to a particle's initial position:
  \begin{equation}
  \langle z^2(t) \rangle = \langle z(t) - z(0) \rangle^2
  \label{eqn:ensemble_msd}
  \end{equation}
  Fits to the ensemble averaged MSD will always reproduce the form of 
  Equation~\ref{eqn:msd_form}. The time-averaged MSD measures all observed 
  displacements over time lag $\tau$: 
  \begin{equation}
  \overline{z^2(\tau)} = \dfrac{1}{T - \tau}\int_{0}^{T - \tau} (z(t + \tau) - z(t))^2 dt
  \label{eqn:tamsd}
  \end{equation}
  where T is the length of the trajectory.

@@

  There are many methods for estimating the Hurst parameter for a time series.
  \cite{clegg_practical_2006} It can be a difficult task because 
  Equation~\ref{eqn:fbm_autocorrelation} decays slowly to zero, especially when 
  $H > 0.5$, meaning one needs to study large time lags with high frequency.
  Fortunately (from a mathematical perspective), all of our solutes show anti-correlated motion, so most of the information in
  Equation~\ref{eqn:fbm_autocorrelation} is contained within the first few time lags (see 
  Figure~\ref{S-fig:hurst_autocorrelation} of the Supplemental Material). Any hope of
  fitting longer time lags to our data is lost in the noise since the analytical values
  are so close to zero. Therefore, we obtained H by performing a least squares fit of 
  Equation~\ref{eqn:fbm_autocorrelation} to the first 
  ten 0.5 ns time lags of the empirically measured autocorrelation function.

@@

  For correlated hops, solute behavior may be described by subordinated
  fractional L\'evy motion (sFLM). The Hurst parameter can again be used to
  describe hop correlations because they share the same autocorrelation
  structure.~\cite{tikanmaki_fractional_2010} The autocovariance function for
  FLM is:
  \begin{equation}
    \gamma(k) = \dfrac{C}{2}\bigg[|k-1|^{2H} - 2|k|^{2H} + |k+1|^{2H}\bigg],
    ~C = \frac{E\big[L(1)^2\big]}{\Gamma(2H + 1)\sin(\pi H)}
    \label{eqn:flm_autocovariance}
  \end{equation}
  where $E\big[L(1)^2\big]$ is the expected value of squared draws from the 
  underlying L\'evy distribution, effectively the distribution's 
  variance.~\cite{bishwal_maximum_2011} In general, most L\'evy stable distributions
  have an undefined variance due to their heavy tails. However, normalizing
  Equation~\ref{eqn:flm_autocovariance} by the variance of a finite number of draws
  from a L\'evy stable distribution results in the same autocorrelation structure as FBM.
  See Section~\ref{S-section:H_estimate} of the Supplemental Material for numerical
  simulations illustrating this point.

  Analogous to power law dwell times, the heavy tails of L\'evy stable hop
  length distributions result in rare but arbitrarily long hops. These long and
  unrealistic hops result in over-estimated simulated MSDs (see
  Figure~\ref{fig:ad_realizations_1mode} for example). We observe that the
  distribution of hops observed in our MD simulations are well approximated by
  L\'evy stable distributions close to the mean, but they significantly
  under-sample the tails. We chose to truncate the L\'evy stable distributions
  based on where the theoretical probability distribution function (PDF) starts
  to deviate from the empirically measured PDF (see
  Section~\ref{S-section:truncation} of the Supplemental
  Material).~\cite{mantegna_stochastic_1994}

  \subsubsection*{Multiple Anomalous Diffusion Regimes}

@@

  \subsubsection*{Simulating Anomalous Diffusion}

@@

  We used Equation~\ref{eqn:tamsd} to calculate the time-averaged MSD of the MD
  and AD model trajectories then estimated their uncertainty using statistical
  bootstrapping. For each bootstrap trial, we randomly chose $n$ solute
  trajectories, where $n$ is the number of independent trajectories, with
  replacement, from the ensemble of trajectories and then calculated the MSD of
  the subset. We reported the time-averaged MSD up to a 1000 ns time lag with
  corresponding 1$\sigma$ confidence intervals.

@@

  We used the Python package \texttt{fbm}~\cite{flynn_fbm_2019} to generate exact simulations of FBM
  and our own Python implementation (see Table~\ref{S-table:python_scripts} of
  the Supplemental Material) of the algorithm by Stoev and Taqqu to
  simulate FLM.~\cite{stoev_simulation_2004} Note that, to our knowledge, there
  are no known exact simulation algorithms for generating FLM trajectories.
  However, the algorithm we used sufficiently approximates draws from the
  marginal L\'evy stable distribution and reasonably approximates the
  correlation structure on MD simulation timescales. We added an empirical
  correction to enhance the accuracy of the correlation structure (see
  Section~\ref{S-section:flm_correlation} of the Supplemental Material for
  validation of the approach).

@@

  We constructed the state transition probability matrix, $T$, based on
  observed solute trajectories. Using methods described in our previous work,
  we determined each solute's radial location and which, if any, trapping
  mechanisms affected it at each time step, then assigned the observation to a
  specific state according to the definitions in
  Table~\ref{table:states}.~\cite{coscia_chemically_2019} Analogous to the mode
  transition matrix in Section~\ref{method:model_sFBM}, and based on the
  current and previous state observation, we incremented the appropriate entry
  of an $n~\times~n$ count matrix by 1, where $n$ is the number of states. We
  verified the Markovianity of state transitions as described in
  Section~\ref{S-section:markov_validation} of the Supplemental Material.

@@

  To derive an analytical equation describing the passage time distributions,
  one can frame the problem as a pulse of particles instantaneously released at
  the pore inlet ($z=0$) which moves at a constant velocity, $v$, and spreads
  out as it approaches $L$. This spreading is parameterized by an effective
  diffusivity parameter, $D$. This approach gives results equivalent to if we
  had released each particle individually and then analyzed the positions of
  the ensemble of trajectories as a function of time. The analytical expression
  describing the distribution of first passage times
  is:~\cite{cussler_diffusion:_2009}
  \begin{equation}
  P(t) = -\frac{1}{\sqrt{\pi}}e^{-(L - vt)^2 / (4Dt)}\bigg(-\frac{D(L - vt)}{4(Dt)^{3/2}} - \frac{v}{2\sqrt{Dt}}\bigg)
  \label{eqn:passage_times}
  \end{equation} 
  where the only free parameters for fitting are $v$ and $D$. A derivation of
  Equation~\ref{eqn:passage_times} is given in
  Section~\ref{S-section:fpt_derivation} of the Supplemental Material. We
  calculated the expected value of Equation~\ref{eqn:passage_times} in order to
  get the MFPT.

@@

  \begin{figure}
  \centering
  % Next 3: /figures/sfbm_distributions
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\textwidth]{gaussian_levy_comparison_anomalous_URE.pdf}
  \caption{}\label{fig:hop_distribution_comparison}
  \end{subfigure}
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\textwidth]{URE_powerlaw.pdf}
  \caption{}\label{fig:powerlaw}
  \end{subfigure}
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\textwidth]{URE_hop_acf.pdf}
  \caption{}\label{fig:hop_acf}
  \end{subfigure}
  \caption{Using urea as an example, (a) the distribution of hop lengths can be
	  fit by a Gaussian in addition to a more general L\'evy stable
	  distribution, though the L\'evy stable distribution does a better job of
	  capturing the heavier tails and increased density near 0. We explore
	  models fit to both distributions, as Gaussian hops are more convenient
	  to model. (b) The distribution of dwell times is fit well by a power
	  law but it over-estimates the probability density at long dwell
	  times. A power law truncated with an exponential cut-off better
	  describes the probability of long dwell times in our simulations. (c)
	  The hops are negatively correlated to their previous hop. In
	  combination, (a) -- (c) support modeling solutes as either
	  subordinated fractional Brownian or L\'evy motion. All other solutes
	  show similar distributions and autocorrelation functions (see
	  Figure~\ref{S-fig:anticorrelated_hops} of the Supplemental Material).
  }\label{fig:anticorrelated_hops}
  \end{figure}

@@

  Several of the choices of AD models and parameters we have described yield
  qualitatively similar trajectories to those seen in our MD simulations.  In
  Figure~\ref{fig:ad_eyetest}, we plot representative sample trajectories for
  each combination of the dwell time and hop distribution, labeled according to
  Table~\ref{table:anomalous_models}. The sFBMcut and sFLMcut in particular
  resemble the trajectories in Figure~\ref{fig:solute_trajectories}.  When we
  do not truncate the dwell time distribution, the trajectories tend to
  incorporate very long dwell times as shown by the sFBM and sFLM models.
  Predictions made with these models consistently under-predict the MD MSDs
  (see Figure~\ref{S-fig:anomalous_msds_bothmode} of the Supplemental
  Material). Therefore, we will not include the pure sFBM or sFLM models in the
  remainder of our analysis.

@@

  We observe that in some cases, solute trajectories extracted from our MD
  simulations display non-stationary behavior. We defined the perceived
  equilibration time point for each solute based on the time at which the
  number of solutes inside the pores and tails stabilized
  (Figure~\ref{S-fig:equilibration}).  With this definition, we observe
  evidence of non-stationary solute behavior after the perceived equilibration
  point, on the $\mu$s timescale. In Table~\ref{table:stationarity}, we compare
  the MSD of the solutes calculated using trajectory data from the first and
  second halves of the ``equilibrated" simulation time. Ethylene glycol and
  methanol show considerable differences between the MSDs of the two halves.
  Urea and acetic acid appear to demonstrate satisfactory stationarity. The
  shapes of urea and acetic acid's MSD curves are also very similar (see
  Figure~\ref{S-fig:msd_comparison} of the Supplemental Material).

@@

  Given stationary data, the AD approach is capable of predicting solute MSDs
  measured from MD simulations within or near statistical uncertainty. In
  Figure~\ref{S-fig:train_test} of the Supplemental Material, we parameterized
  the AD models using the first half of the stationary solute equilibrated
  trajectories and then compared the model predictions to the MD MSD of the
  second half of the stationary trajectories. In most cases, the model
  predictions fall within the 1$\sigma$ confidence intervals of the MD MSD.

@@

  We obtain reasonable predictions of the MD simulated MSDs when we
  parameterize AD models with all available data after the perceived
  equilibration time. The MSD curves generated from both the one and 
  two mode models are overlayed with the MD simulated MSDs for comparison in
  Figure~\ref{fig:anomalous_msds}. The associated parameters for the one and two
  mode models are presented in Figures~\ref{fig:1mode_parameters}
  and~\ref{fig:2mode_parameters}.

@@

  The deviation between the one mode MSD predictions and MD are primarily due
  to differences in their curvature at long time lags. The shape and magnitude
  of the predicted curves appears accurate relative to MD at short time lags.
  However, the modeled trajectories undershoot the mean MD MSD as the time lag
  increases. As discussed in the previous section, long time positional
  anti-correlation, on the order of hundreds of ns, may not exist in the MD
  system. Eventual loss of correlation would result in a shift from sub-linear
  to linear MSD behavior, as observed in the MD trajectories. Acetic acid
  exemplifies this point. At first glance, acetic acid's predicted MSD appears
  to match the curvature of MD quite well, but closer examination reveals that
  the MD MSD curve may actually shift from a sub-linear to a linear regime around
  500 ns.

@@

  \section*{Supplemental Material}

  Detailed explanations and expansions upon the results and procedures
  mentioned in the main text are described in the Supplemental Material. This
  information is available free of charge via the Internet at
  http://pubs.acs.org.

  \section*{Acknowledgments}

>>>>

\chapter{Capturing Subdiffusive Solute Dynamics and Predicting Selectivity in Nanoscale Pores
  with Time Series Modeling}

@@

  In our previous work,~\cite{coscia_chemically_2019} we used molecular
  dynamics (MD) simulations to study the transport of 20 small polar molecules
  in an H\textsubscript{II} phase LLC membrane. We chose to study the
  H\textsubscript{II} phase because it is a simpler geometry to model than the
  Q\textsubscript{I} phase and significantly more structural data is available
  to help ensure molecular models are consistent with experiment. 
  %BJCF: modified  
  %In general,
  On MD simulation timescales, 
  we observed subdiffusive transport behavior characterized by intermittent
  hops separated by periods of entrapment. We identified three mechanisms
  responsible for the solute trapping behavior: entanglement among monomer
  tails, hydrogen bonding with monomer head groups, and association with the
  monomer's sodium counter ions.

@@

  We constructed our first model by applying the existing rigorous theoretical
  foundation which describes the motion of particles that exhibit non-Brownian,
  or anomalous, transport behavior.~\cite{metzler_random_2000,bouchaud_anomalous_1990} The tools
  introduced by fractional calculus are instrumental to this
  theory.~\cite{gorenflo_fractional_1997} They allow us to generalize the
  normally linear diffusion equation to fractional derivative orders, providing
  descriptions of a much more diverse set of behavior, including subdiffusion,
  a type of anomalous diffusion exhibited by solutes
  %in this study.~\cite{klages_anomalous_2008}
  %BJCF: modified
  on the simulation timescales of this study.~\cite{klages_anomalous_2008}

@@

  We ran all MD simulations and energy minimizations using GROMACS
  2018~\cite{bekker_gromacs:_1993,berendsen_gromacs:_1995,van_der_spoel_gromacs:_2005,hess_gromacs_2008}.
  We performed all post-simulation trajectory analysis using Python scripts
  which are available online at \\
  \texttt{https://github.com/shirtsgroup/LLC\_Membranes}.  The appropriate
  scripts to use for subsequent calculations are summarized in
  Table~\ref{table:python_scripts} of Appendix C.

@@

  We considered each system to be equilibrated when the solute partitioning between the 
  pore and tail region reached apparent equilibrium and use only data after that point
  in our analysis of solute kinetics. We plot the solute partition versus time in
  Figure~\ref{fig:equilibration} of Appendix C in order to justify
  our choice of equilibration times for each solute.

@@

  %BJCF: added
  On the timescales simulated in this study,
  solutes in this system very clearly exhibit subdiffusive behavior, a type of
  anomalous diffusion. During an anomalous diffusion process, the mean squared 
  displacement (MSD) does not grow linearly with time, but instead it follows 
  a power law of the form: 
  \begin{equation} 
  \langle z^2(t) \rangle = K_{\alpha}t^{\alpha}
  \label{eqn:msd_form}
  \end{equation} 
  where $\alpha$ is the anomalous exponent and $K_{\alpha}$ is the generalized 
  diffusion coefficient. In this work, we only consider the MSD with respect to
  the solutes' center of mass $z$-coordinate, which is oriented along the pore 
  axis. A value of $\alpha < 1$ indicates a subdiffusive process, while values
  of $\alpha = 1$ and $\alpha > 1$ are characteristic of Brownian and 
  superdiffusive motion respectively.

  While it is theoretically possible to extract the value of $\alpha$ by fitting
  Equation~\ref{eqn:msd_form} to an MSD generated directly from MD simulations, 
  we do not simulate enough independent solute trajectories to obtain a reliable
  estimate. 
  %BJCF: added next two sentences
  It is also possible that solute dynamics will become diffusive on
  long simulation timescales. Therefore, the transition from subdiffusion to regular
  diffusion may interfere with estimates of $\alpha$ obtained by fitting to the MSD curves. 
  We can obtain higher precision estimates of $\alpha$ using the dwell
  time distributions described in subsequent sections.

@@

  One can measure MSD in two ways. The ensemble averaged MSD measures 
  displacements with respect to a particle's initial position:
  \begin{equation}
  \langle z^2(t) \rangle = \langle z(t) - z(0) \rangle^2
  \label{eqn:ensemble_msd2}
  \end{equation}
  Fits to the ensemble averaged MSD will always reproduce the form of 
  Equation~\ref{eqn:msd_form}. The time-averaged MSD measures all observed 
  displacements over time lag $\tau$: 
  \begin{equation}
  \overline{z^2(\tau)} = \dfrac{1}{T - \tau}\int_{0}^{T - \tau} (z(t + \tau) - z(t))^2 dt
  \label{eqn:tamsd2}
  \end{equation}
  where T is the length of the trajectory.

@@

  There are many methods for estimating the Hurst parameter for a time series.
  \cite{clegg_practical_2006} It can be a difficult task because 
  Equation~\ref{eqn:fbm_autocorrelation} decays slowly to zero, especially when 
  $H > 0.5$, meaning one needs to study large time lags with high frequency.
  Fortunately (from a mathematical perspective), all of our solutes show anti-correlated motion, so most of the information in
  Equation~\ref{eqn:fbm_autocorrelation} is contained within the first few time lags (see 
  Figure~\ref{fig:hurst_autocorrelation} of Appendix C). Any hope of
  fitting longer time lags to our data is lost in the noise since the analytical values
  are so close to zero. Therefore, we obtained H by performing a least squares fit of 
  Equation~\ref{eqn:fbm_autocorrelation} to the first 
  ten 0.5 ns time lags of the empirically measured autocorrelation function.

@@

  For correlated hops, solute behavior may be described by subordinated
  fractional L\'evy motion (sFLM). The Hurst parameter can again be used to
  describe hop correlations because they share the same autocorrelation
  structure.~\cite{tikanmaki_fractional_2010} The autocovariance function for
  FLM is:
  \begin{equation}
    \gamma(k) = \dfrac{C}{2}\bigg[|k-1|^{2H} - 2|k|^{2H} + |k+1|^{2H}\bigg],
    ~C = \frac{E\big[L(1)^2\big]}{\Gamma(2H + 1)\sin(\pi H)}
    \label{eqn:flm_autocovariance}
  \end{equation}
  where $E\big[L(1)^2\big]$ is the expected value of squared draws from the 
  underlying L\'evy distribution, effectively the distribution's 
  variance.~\cite{bishwal_maximum_2011} In general, most L\'evy stable distributions
  have an undefined variance due to their heavy tails. However, normalizing
  Equation~\ref{eqn:flm_autocovariance} by the variance of a finite number of draws
  from a L\'evy stable distribution results in the same autocorrelation structure as FBM.
  See Section~\ref{section:H_estimate} of Appendix C for numerical
  simulations illustrating this point.

  Analogous to power law dwell times, the heavy tails of L\'evy stable hop
  length distributions result in rare but arbitrarily long hops. These long and
  unrealistic hops result in over-estimated simulated MSDs (see
  Figure~\ref{fig:ad_realizations_1mode} for example). We observe that the
  distribution of hops observed in our MD simulations are well approximated by
  L\'evy stable distributions close to the mean, but they significantly
  under-sample the tails. We chose to truncate the L\'evy stable distributions
  based on where the theoretical probability distribution function (PDF) starts
  to deviate from the empirically measured PDF (see
  Section~\ref{section:truncation} of Appendix C).~\cite{mantegna_stochastic_1994}

  \subsubsection{Multiple Anomalous Diffusion Regimes}

@@

  \subsubsection{Simulating Anomalous Diffusion}

@@

  We used Equation~\ref{eqn:tamsd2} to calculate the time-averaged MSD of the MD
  and AD model trajectories then estimated their uncertainty using statistical
  bootstrapping. For each bootstrap trial, we randomly chose $n$ solute
  trajectories, where $n$ is the number of independent trajectories, with
  replacement, from the ensemble of trajectories and then calculated the MSD of
  the subset. We reported the time-averaged MSD up to a 1000 ns time lag with
  corresponding 1$\sigma$ confidence intervals.

@@

  We used the Python package \texttt{fbm}~\cite{flynn_fbm_2019} to generate exact simulations of FBM
  and our own Python implementation (see Table~\ref{table:python_scripts} of
  Appendix C) of the algorithm by Stoev and Taqqu to
  simulate FLM.~\cite{stoev_simulation_2004} Note that, to our knowledge, there
  are no known exact simulation algorithms for generating FLM trajectories.
  However, the algorithm we used sufficiently approximates draws from the
  marginal L\'evy stable distribution and reasonably approximates the
  correlation structure on MD simulation timescales. We added an empirical
  correction to enhance the accuracy of the correlation structure (see
  Section~\ref{section:flm_correlation} of Appendix C for
  validation of the approach).

@@

  We constructed the state transition probability matrix, $T$, based on
  observed solute trajectories. Using methods described in our previous work,
  we determined each solute's radial location and which, if any, trapping
  mechanisms affected it at each time step, then assigned the observation to a
  specific state according to the definitions in
  Table~\ref{table:states}.~\cite{coscia_chemically_2019} Analogous to the mode
  transition matrix in Section~\ref{method:model_sFBM}, and based on the
  current and previous state observation, we incremented the appropriate entry
  of an $n~\times~n$ count matrix by 1, where $n$ is the number of states. We
  verified the Markovianity of state transitions as described in
  Section~\ref{section:markov_validation} of Appendix C.

@@

  To derive an analytical equation describing the passage time distributions,
  one can frame the problem as a pulse of particles instantaneously released at
  the pore inlet ($z=0$) which moves at a constant velocity, $v$, and spreads
  out as it approaches $L$. This spreading is parameterized by an effective
  diffusivity parameter, $D$. This approach gives results equivalent to if we
  had released each particle individually and then analyzed the positions of
  the ensemble of trajectories as a function of time. The analytical expression
  describing the distribution of first passage times
  is:~\cite{cussler_diffusion:_2009}
  \begin{equation}
  P(t) = -\frac{1}{\sqrt{\pi}}e^{-(L - vt)^2 / (4Dt)}\bigg(-\frac{D(L - vt)}{4(Dt)^{3/2}} - \frac{v}{2\sqrt{Dt}}\bigg)
  \label{eqn:passage_times}
  \end{equation} 
  where the only free parameters for fitting are $v$ and $D$. A derivation of
  Equation~\ref{eqn:passage_times} is given in
  Section~\ref{section:fpt_derivation} of Appendix C. We
  calculated the expected value of Equation~\ref{eqn:passage_times} in order to
  get the MFPT.

@@

  \begin{figure}
  \centering
  % Next 3: /figures/sfbm_distributions
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\textwidth]{gaussian_levy_comparison_anomalous_URE.pdf}
  \caption{}\label{fig:hop_distribution_comparison}
  \end{subfigure}
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\textwidth]{URE_powerlaw.pdf}
  \caption{}\label{fig:powerlaw}
  \end{subfigure}
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\textwidth]{URE_hop_acf.pdf}
  \caption{}\label{fig:hop_acf}
  \end{subfigure}
  \caption{Using urea as an example, (a) the distribution of hop lengths can be
	  fit by a Gaussian in addition to a more general L\'evy stable
	  distribution, though the L\'evy stable distribution does a better job of
	  capturing the heavier tails and increased density near 0. We explore
	  models fit to both distributions, as Gaussian hops are more convenient
	  to model. (b) The distribution of dwell times is fit well by a power
	  law but it over-estimates the probability density at long dwell
	  times. A power law truncated with an exponential cut-off better
	  describes the probability of long dwell times in our simulations. (c)
	  The hops are negatively correlated to their previous hop. In
	  combination, (a) -- (c) support modeling solutes as either
	  subordinated fractional Brownian or L\'evy motion. All other solutes
	  show similar distributions and autocorrelation functions (see
	  Figure~\ref{fig:anticorrelated_hops} of Appendix C).
  }\label{fig:anticorrelated_hops}
  \end{figure}

@@

  Several of the choices of AD models and parameters we have described yield
  qualitatively similar trajectories to those seen in our MD simulations.  In
  Figure~\ref{fig:ad_eyetest}, we plot representative sample trajectories for
  each combination of the dwell time and hop distribution, labeled according to
  Table~\ref{table:anomalous_models}. The sFBMcut and sFLMcut in particular
  resemble the trajectories in Figure~\ref{fig:solute_trajectories}.  When we
  do not truncate the dwell time distribution, the trajectories tend to
  incorporate very long dwell times as shown by the sFBM and sFLM models.
  Predictions made with these models consistently under-predict the MD MSDs
  (see Figure~\ref{S-fig:anomalous_msds_bothmode} of Appendix C). Therefore, we 
  will not include the pure sFBM or sFLM models in the remainder of our analysis.

@@

  We observe that in some cases, solute trajectories extracted from our MD
  simulations display non-stationary behavior. We defined the perceived
  equilibration time point for each solute based on the time at which the
  number of solutes inside the pores and tails stabilized
  (Figure~\ref{fig:equilibration}).  With this definition, we observe
  evidence of non-stationary solute behavior after the perceived equilibration
  point, on the $\mu$s timescale. In Table~\ref{table:stationarity}, we compare
  the MSD of the solutes calculated using trajectory data from the first and
  second halves of the ``equilibrated" simulation time. Ethylene glycol and
  methanol show considerable differences between the MSDs of the two halves.
  Urea and acetic acid appear to demonstrate satisfactory stationarity. The
  shapes of urea and acetic acid's MSD curves are also very similar (see
  Figure~\ref{fig:msd_comparison} of Appendix C).

@@

  Given stationary data, the AD approach is capable of predicting solute MSDs
  measured from MD simulations within or near statistical uncertainty. In
  Figure~\ref{fig:train_test} of Appendix C, we parameterized
  the AD models using the first half of the stationary solute equilibrated
  trajectories and then compared the model predictions to the MD MSD of the
  second half of the stationary trajectories. In most cases, the model
  predictions fall within the 1$\sigma$ confidence intervals of the MD MSD.

@@

  We obtain reasonable predictions of the MD simulated MSDs when we
  parameterize AD models with all available data after the perceived
  equilibration time. The MSD curves generated from both the one and 
  two mode models are overlaid with the MD simulated MSDs for comparison in
  Figure~\ref{fig:anomalous_msds}. The associated parameters for the one and two
  mode models are presented in Figures~\ref{fig:1mode_parameters}
  and~\ref{fig:2mode_parameters}.

@@

  The deviation between the one mode MSD predictions and MD are primarily due
  to differences in their curvature at long time lags. The shape and magnitude
  of the predicted curves appears accurate relative to MD at short time lags.
  However, the modeled trajectories undershoot the mean MD MSD as the time lag
  increases. 
  %BJCF: I don't think this is discussed in the previous section.
  % As discussed in the previous section, 
  %BJCF: Rest of this paragraph already addresses Matt's point. I added "...,or subdiffusive,...,or diffusive," to make explicit
  Long time positional anti-correlation, on the order of hundreds of ns, may not
  exist in the MD system. Eventual loss of correlation would result in a shift from
  sub-linear, or subdiffusive, to linear, or diffusive, MSD behavior, as observed in the MD trajectories.   
  Acetic acid exemplifies this point. At first glance, acetic acid's predicted MSD appears
  to match the curvature of MD quite well, but closer examination reveals that
  the MD MSD curve may actually shift from a sub-linear to a linear regime around
  500 ns.

@@
